A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2019-04-30 doc/large_strain.tex
put tables inside the main tex so that arXiv is not tyring to build them separately

\input{parallelization_2d.tex}
\input{parallelization_3d.tex}

@@

\input{weak_scaling_3d.tex}

>>>>

\begin{table}
  \centering
  \resizebox{\textwidth}{!}{
  \begin{tabular}{|c|cc|ccc|ccc|ccc|}
  \hline
                & \multicolumn{2}{c|}{serial} & \multicolumn{3}{c|}{MPI} & \multicolumn{3}{c|}{SIMD} & \multicolumn{3}{c|}{MPI+SIMD}  \\
  \hline
  p             & time  & GFlop/s              & time & GFlop/s & speedup & time & GFlop/s & speedup & time & GFlop/s & speedup \\
  \hline
  2& \pgfmathprintnumber{0.71685} & \pgfmathprintnumber{0.8747712} & \pgfmathprintnumber{0.07427} & \pgfmathprintnumber{8.57318} & \pgfmathprintnumber{9.65194560388} & \pgfmathprintnumber{0.3939} & \pgfmathprintnumber{1.6528706} & \pgfmathprintnumber{1.81987814166} & \pgfmathprintnumber{0.04142} & \pgfmathprintnumber{16.0073657} & \pgfmathprintnumber{17.306856591} \\
  4& \pgfmathprintnumber{0.47603} & \pgfmathprintnumber{1.3088965} & \pgfmathprintnumber{0.0511} & \pgfmathprintnumber{12.3860771} & \pgfmathprintnumber{9.3156555773} & \pgfmathprintnumber{0.25747} & \pgfmathprintnumber{2.3690572} & \pgfmathprintnumber{1.84887559716} & \pgfmathprintnumber{0.02786} & \pgfmathprintnumber{22.2420699} & \pgfmathprintnumber{17.0865039483} \\
  6& \pgfmathprintnumber{0.24683} & \pgfmathprintnumber{1.5497601} & \pgfmathprintnumber{0.02636} & \pgfmathprintnumber{14.8125524} & \pgfmathprintnumber{9.36380880121} & \pgfmathprintnumber{0.13089} & \pgfmathprintnumber{2.8544567} & \pgfmathprintnumber{1.88578195431} & \pgfmathprintnumber{0.01487} & \pgfmathprintnumber{26.0509717} & \pgfmathprintnumber{16.5991930061} \\
  \hline
  \end{tabular}
  }
  \caption{Wall-clock time in seconds and performance in GFlops of Algorithm \ref{alg:mf_tensor4} in 2D for various combinations of polynomial degrees,
  vectorization and parallelization.}
  \label{tab:numbers_2d}
\end{table}

\begin{table}
  \centering
  \resizebox{\textwidth}{!}{
  \begin{tabular}{|c|cc|ccc|ccc|ccc|}
  \hline
                & \multicolumn{2}{c|}{serial} & \multicolumn{3}{c|}{MPI} & \multicolumn{3}{c|}{SIMD} & \multicolumn{3}{c|}{MPI+SIMD}  \\
  \hline
  p             & time  & GFlop/s              & time & GFlop/s & speedup & time & GFlop/s & speedup & time & GFlop/s & speedup \\
  \hline
  2& \pgfmathprintnumber{1.82927} & \pgfmathprintnumber{1.4408182} & \pgfmathprintnumber{0.19184} & \pgfmathprintnumber{13.75528} & \pgfmathprintnumber{9.5353940784} & \pgfmathprintnumber{1.24738} & \pgfmathprintnumber{2.2390063} & \pgfmathprintnumber{1.46648976254} & \pgfmathprintnumber{0.13397} & \pgfmathprintnumber{21.0187594} & \pgfmathprintnumber{13.6543255953} \\
  4& \pgfmathprintnumber{1.14988} & \pgfmathprintnumber{1.7483867} & \pgfmathprintnumber{0.1211} & \pgfmathprintnumber{16.6162812} & \pgfmathprintnumber{9.49529314616} & \pgfmathprintnumber{0.74974} & \pgfmathprintnumber{2.7527409} & \pgfmathprintnumber{1.53370501774} & \pgfmathprintnumber{0.08166} & \pgfmathprintnumber{25.4865287} & \pgfmathprintnumber{14.0813127602} \\
  \hline
  \end{tabular}
  }
  \caption{Wall-clock time in seconds and performance in GFlops of Algorithm \ref{alg:mf_tensor4} in 3D for various combinations of polynomial degrees,
  vectorization and parallelization.}
  \label{tab:numbers_3d}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{|r|r|c|r|c|}
  \hline
  cores  & $N_{DoF}$ & $N_{gref}$ & vmult [s] & CG [s / iteration] \\
  \hline
  20 & 4,442,880 & 3 & \pgfmathprintnumber{0.0675} & \pgfmathprintnumber{0.529553679131} \\
  160 & 35,071,488 & 4 & \pgfmathprintnumber{0.0705} & \pgfmathprintnumber{0.562637362637} \\
  1280 & 278,694,912 & 5 & \pgfmathprintnumber{0.083} & \pgfmathprintnumber{0.688792165397} \\
  \hline
  \end{tabular}
  \caption{Weak scaling of Algorithm \ref{alg:mf_tensor4} in 3D for quadratic polynomial basis.}
  \label{tab:weak_3d}
\end{table}
